---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# calcDOsat

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

This package will calculate dissolved oxygen saturation given water temperature, barometric pressure, and dissolved oxygen concentration. Solubility equations for oxygen in water are taken from the USGS Technical Memorandum 2011.03.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("biogeochem/calcDOsat")
```
## Example

Add the DO saturation percent the `data.frame` of field or lab data with the `'weiss'`, `'benson_krause'` or `'garcia_gordon'` methods:


```{r example}
library(calcDOsat)

# create example data
dat <- data.frame(Temp_C = 20, Baro_kPa = 101.325, Spec_Cond_uS.cm = 0, DO_mg.L = 8)

# add calculated DO saturation percent
dat <- calcDOsat(dat, 'weiss', 'Temp_C', 'Baro_kPa', 'Spec_Cond_uS.cm', 'DO_mg.L')
```
